---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mypackage

<!-- badges: start -->
<!-- badges: end -->

The purpose of mypackage is to allow you to explore where your US tax dollars are going. 
Within the app, you input your income for the year and your marital status. The app 
then calculates your estimated federal taxes paid and where those dollars went.

## Installation

You can install the development version of mypackage from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-trut0001")
```

## Use

To use the app, simply load the library and then run the app with the following command: 

```{r example, eval = FALSE}
library(mypackage)
mypackage::run_app()
```

For more detailed instructions, see the vignette:

```{r vignette_link, eval = FALSE}
vignette("introduction", package = "mypackage")
```

