---
title: "US Federal Tax Explorer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(usfederaltaxexplorer)
```

## Introduction to `usfederaltaxexplorer`

`usfederaltaxexplorer` provides Shiny app that allows users to input their yearly income and filing status to see what their tax dollars are funding.

This vignette will walk you through how to install the package, load the data, and use the Shiny app.

## Install `usfederaltaxexplorer` from GitHub
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
remotes::install_github("trut0001/usfederaltaxexplorer")

## Data

There is no data to download or access. This is a low barrier app that you can use immediately. 

## Launch the Shiny app

To launch the app, simply enter the following in the R console:

usfederaltaxexplorer::run_app()

## Using the Shiny App

After launching the app using `usfederaltaxexplorer::run_app()`, follow these steps:

1. **Enter your yearly income**: Provide your annual income in USD.
2. **Select your filing status**: Choose between "Single" or "Married Jointly".
3. **Click "Calculate"**: The app will show how your federal tax dollars are distributed across key programs.

## Interpreting the Results
- The table displays the amount (in USD) allocated to various programs such as healthcare, defense, and education.
- Use these insights to understand how your tax dollars are being spent.

## More Information

For further information, visit the [pkgdown site](https://yourusername.github.io/mypackage) or the [official documentation](https://pkgdown.yoursite.com/).
